Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-05 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Comment out for now talks that have no summaries.

Lightning talks were a new feature in WSSSPE2. Since the workshop program was
mostly dedicated to discussions, the organizers wanted to give the attendees a
chance to also `make a pitch' for an idea, either representing a contributed paper
or something different.  Eighteen attendees volunteered to participate in the lightning
talks, each given only two minutes to speak and at most one slide to show.
The talks were presented in reverse alphabetic order of speakers' last names. 
In the rest of this session, we highlight the gist of the speakers' key messages.

\begin{enumerate}
\item Greg Wilson: Close Enough for Scientific Work

@@

\item James Spencer: Developing New Developers

\item Erin Robinson:  Sustaining Science Bazaars

@@

\item John W Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub

\item Abani Patra: Execute it

\item Christopher Lenhardt: Open Science for Synthesis (OSS): Filling the Gap in
Early Career Training

\item Daniel S. Katz: Implementing Transitive Credit with JSON-LD

\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software

@@

\item Sarah Harris: Sustainability of Multidisciplinary Software: A Science
Perspective

\item Marcus D. Hanwell: We Need Tool Builders for Sustainable Scientific
Software

\item Ted Habermann: Communities as the Whole Product

\item Robert R. Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices

@@

\item Jakob Blomer: The Need for a Versioned Data Analysis Environment

>>>>

Lightning talks were a new feature in WSSSPE2. Since the workshop program was
mostly dedicated to discussions, the organizers wanted to give the attendees a
chance to also `make a pitch' for an idea, either representing a contributed paper
or something different.  Eighteen attendees volunteered to participate in the lightning
talks, each given only two minutes to speak and at most one slide to show.
The talks were presented in reverse alphabetic order of speakers' last names. 
In the rest of this session, we highlight the gist of some of the speakers' messages.

\begin{enumerate}
%\item Greg Wilson: Close Enough for Scientific Work

@@

%\item James Spencer: Developing New Developers

%\item Erin Robinson:  Sustaining Science Bazaars

@@

%\item John W Peterson: Continuous Integration for Concurrent MOOSE Framework and
%Application Development on GitHub

%\item Abani Patra: Execute it

%\item Christopher Lenhardt: Open Science for Synthesis (OSS): Filling the Gap in
%Early Career Training

%\item Daniel S. Katz: Implementing Transitive Credit with JSON-LD

%\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software

@@

%\item Sarah Harris: Sustainability of Multidisciplinary Software: A Science
%Perspective

%\item Marcus D. Hanwell: We Need Tool Builders for Sustainable Scientific
%Software

%\item Ted Habermann: Communities as the Whole Product

%\item Robert R. Downs: Community Recommendations for Improving Sustainable
%Scientific Software Practices

@@

% \item Jakob Blomer: The Need for a Versioned Data Analysis Environment
